---
title: "Python code chunks in R Markdown"
author: "Michael Knous"
date: "November 21, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Sys.setenv(PATH = paste("d:\\anaconda35",Sys.getenv("PATH"),sep=";"))
library(reticulate)
path_to_python <- ("d:\\anaconda35\\python")
use_python(path_to_python)
knitr::knit_engines$set(python = reticulate::eng_python)
py_available(initialize = TRUE)

```


## A normal R Code Chunk

```{r}

x=42
print(x)
```

## modify an R variable

In the following chunk, the value of `x` on the right hand side is `r x`, which was defined in the previous chunk

```{r}
x = x+12
print(x)
```

## A python chunk

This works fine and as expected

```{python}
x = 42*2
print(x)
```

The value of `x` in the Python session is `r py$x`.
It is not the same `x` as the one in R.

## Modify a Python variable

```{python}
x = x + 18
print(x)
```

Retrieve the value of `x` from the Python session again:

```{r}
py$x
```

Assign to a variable in the Python session from R:

```{r}
py$y = 1:5
```

See the value of `y` in the Python session:

```{python}
print(y)
```

##Python graphics

You can draw plots using the **matplotlib** package in Python.

```{python}
import matplotlib.pyplot as plt
plt.plot([0,2,1,4])
plt.show()
```

```{python}
import sys
print(sys.version)
```

